|

### 2023-01-16 paper_comparison/paper_comparison/paper_comparison.Rmd
feedback from the meeting

In hypothesis testing, $p$-value is defined as the probability of observing test results as least as extreme as the observed result given $H_0$ is true. Within the context of visual inference, by involving $k$ independent observers, $p$-value can be interpreted as the probability of having as many or more subjects detect the data plot than the observed result.

@@

@@

@@

@@

@@

>>>>

In hypothesis testing, a $p$-value is defined as the probability of observing test results as least as extreme as the observed result given $H_0$ is true. Within the context of visual inference, by involving $k$ independent observers, the $p$-value can be interpreted as the probability of having as many or more subjects detect the data plot than the observed result.

@@

(definition of power, apply it to visual test)

@@

(put easy, moderate, difficult in caption)

(aspect ratio of mosaic plot)

(set the threshold of RESET -> higher)

(own: inspect the power of RESET for higher order only)

(own: power of BP on butterfly shape, triangle shape, etc)

(remove lineup id from caption)

@@

p_value_cmp_dat %>%
  filter(x_dist == "uniform") %>%
  ggplot() +
  ggmosaic::geom_mosaic(aes(x = ggmosaic::product(reject, conv_reject), fill = reject)) +
  facet_grid(~type) +
  ylab("Visual tests") +
  xlab("Conventional tests") +
  labs(fill = "Conventional tests") +
  scale_fill_brewer("", palette="Dark2") +
  theme_bw() +
  theme(legend.position = "none")

p_value_cmp_dat %>%
  filter(x_dist == "uniform") %>%
  filter(difficulty == "easy") %>%
  ggplot() +
  ggmosaic::geom_mosaic(aes(x = ggmosaic::product(reject, conv_reject), fill = reject)) +
  facet_grid(~type) +
  ylab("Visual tests") +
  xlab("Conventional tests") +
  labs(fill = "Conventional tests") +
  scale_fill_brewer("", palette="Dark2") +
  theme_bw() +
  theme(legend.position = "none") +
  ggtitle("Easy") -> p1

p_value_cmp_dat %>%
  filter(x_dist == "uniform") %>%
  filter(difficulty == "moderate") %>%
  ggplot() +
  ggmosaic::geom_mosaic(aes(x = ggmosaic::product(reject, conv_reject), fill = reject)) +
  facet_grid(~type) +
  ylab("Visual tests") +
  xlab("Conventional tests") +
  labs(fill = "Conventional tests") +
  scale_fill_brewer("", palette="Dark2") +
  theme_bw() +
  theme(legend.position = "none") +
  ylab("") +
  ggtitle("Moderate") -> p2

p_value_cmp_dat %>%
  filter(x_dist == "uniform") %>%
  filter(difficulty == "difficult") %>%
  ggplot() +
  ggmosaic::geom_mosaic(aes(x = ggmosaic::product(reject, conv_reject), fill = reject)) +
  facet_grid(~type) +
  ylab("Visual tests") +
  xlab("Conventional tests") +
  labs(fill = "Conventional tests") +
  scale_fill_brewer("", palette="Dark2") +
  theme_bw() +
  theme(legend.position = "none") +
  ylab("") +
  ggtitle("Difficult") -> p3

@@

(uniform base line : grey)

(grey not work great with green)

(use different color pal)

(calc the diff in power and plot)

(randomly subset uniform and check the change of the power)

@@

(discrete is the lowest for non-linearity: discreteness makes people harder to connect the shape? People focus on other features such as outliers instead of the shape? If this is the case, more evaluations may lead to a reject. We need some examples (log(E) > 4) here)

```{r eval = FALSE}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(type == "polynomial") %>%
  filter(x_dist == "even_discrete") %>%
  filter(log(effect_size) > 4) %>%
  filter(p_value > 0.05) %>%
  .$unique_lineup_id %>%
  unique()
```

```{r eval = FALSE}
VI_MODEL$plot_lineup(vi_lineup$poly_64$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

In the case of non-linearity model,

It can be observed that because of the visibility of the visual pattern, the discrete uniform distribution

visual test
